Recursive algorithms and branching for nonmaximal embeddings

### 2010-11-18 AffineLieAlgebras/InformalNotes/article.tex
Incorporate V.D. changes of 12.11

\documentclass[12pt]{iopart}
%\usepackage{ucs}
%\usepackage{amsmath,amssymb,amsthm}
\usepackage{iopams,amssymb,amsthm}
%\usepackage{pb-diagram}
\usepackage{multicol}
%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage{color}
\usepackage{graphicx}
\usepackage{epstopdf}
%\usepackage{graphicx}
%\pagestyle{plain}
%\usepackage[unicode,verbose,plainpages=false]{hyperref}
\usepackage{hyperref}

@@

\newtheorem{statement}{Statement}
\newtheorem{theorem}{Theorem}
%\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}{Lemma}
\newtheorem{mynote}{Note}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}

@@

\title{Recursive algorithms, branching coefficients and applications}
\author{V D Lyakhovsky$^1$ and A A Nazarov$^2$}
\address{$^{1,2}$ Theoretical Department, SPb State University,
198904, Sankt-Petersburg, Russia }
\eads{$^1$ \mailto{lyakh1507@nm.ru}, $^2$ \mailto{antonnaz@gmail.com}}

\begin{abstract}
  Recurrent relations for branching coefficients in affine Lie algebras integrable highest weight modules are studied. The decomposition algorithm based on the injection fan technique is adopted to the situation where the Weyl denominator becomes singular with respect to a reductive subalgebra. We study some modifications of the injection fan technique and demonstrate that it is possible to define the "subtracted fans" that play the role similar to the original ones. Possible applications of subtracted fans in CFT models are considered.
\end{abstract}
\ams{17B67, 17B10}
\submitto{\JPA}
%\maketitle

@@

There exist several different approaches to deal with the branching coefficients. Some of them use the BGG
resolution \cite{bernstein1975differential} (for Kac-Moody algebras the algorithm is described in
\cite{kac1990idl},\cite{wakimoto2001idl}), the Schur function series \cite{fauser2006new}, the BRST
cohomology \cite{Hwang:1994yr}, Kac-Peterson formulas \cite{kac1990idl,quella2002branching} or the
combinatorial methods applied in \cite{feigin707principal}.

Usually only the maximal reductive subalgebras are considered since the case of non-maximal subalgebra
can be obtained using the chain of maximal injections. In this paper we find the recurrent properties
for branching coefficients that generalize the relations obtained earlier (see the paper \cite{ilyin812pbc}
and the references therein) to the case of non-maximal reductive subalgebra. The result is formulated in
terms of the new injection fan called "the subtracted fan". Using this new tools we formulate a simple and
explicit algorithm for computations of branching coefficients which is applicable to the non-maximal
subalgebras of finite-dimensional and affine Lie algebras.

@@

The paper is organised as follows. In the subsection \ref{sec:notation}  we fix the notations.
In the Section \ref{sec:recurr-form-branch} we derive the subtracted recurrent formula for anomalous
branching coefficients and describe the decomposition algorithm for integrable highest weight modules
$L_{\mathfrak{g}}$ with respect to a reductive subalgebra $\mathfrak{a}\subset \mathfrak{g}$
(subsection \ref{sec:algorithm}). In the Section \ref{sec:finite-dimens-lie} we present several
simple examples for finite-dimensional Lie algebras. The affine Lie algebras and their applications in
CFT models are considered in Section \ref{sec:phys-appl}.
Possible further developments are discussed (Section \ref{sec:conclusion}).

@@

$\co{\Delta}$ , $\left( \co{\Delta _{\af}}%
\right)$ --- the finite root system of the subalgebra $\co{%
\frak{g}}$ (resp. $\co{\af}$);
$\Theta$, $(\Theta_{\mathfrak{a}})$ --- the highest root of the algebra $\mathfrak{g}$ (resp. subalgebra $\mathfrak{a}$);

@@

$M \left( \mbox{resp. }M_{\af}\right) :=$

\noindent $=\left\{
\begin{array}{c}
\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}^{\vee }\mbox{ }\left( \mbox{resp. }%
\sum_{i=1}^{r}\mathbf{Z}\alpha _{\left( \af\right) i}^{\vee }\right)
\mbox{for untwisted algebras or }A_{2r}^{\left( 2\right) }, \\
\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}\mbox{ }\left( \mbox{resp. }\sum_{i=1}^{r}%
\mathbf{Z}\alpha _{\left( \af\right) i}\right) \mbox{for }A_{r}^{\left(
u\geq 2\right) }\mbox{ and }A\neq A_{2r}^{\left( 2\right) },
\end{array}
\right\} ;$\\
$\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu +\rho )-\rho }$ --- the singular weight element for the $\frak{g}$-module $L^{\mu }$;
$\Psi _{\left( \af\right) }^{\left( \nu \right) }:=\sum\limits_{w\in W_{\af}}\epsilon (w)e^{w\circ (\nu +\rho
_{_{\af}})-\rho _{_{\af}}}$ --- the corresponding singular weight
element for the $\af$-module $L_{\af}^{\nu }$;

$\widehat{\Psi ^{\left( \mu \right) }}$ $\left( \widehat{\Psi _{\left( \frak{%
a}\right) }^{\left( \nu \right) }}\right) $ --- the set of singular weights $%
\xi \in P$ $\left( \mbox{resp. }\in P_{\af}\right) $ for the module $%
L^{\mu }$ $\left( \mbox{resp. }L_{\af}^{\nu }\right) $ with the
coordinates $\left( \co{\xi },k,n,\epsilon \left( w\left( \xi
\right) \right) \right) \mid _{\xi =w\left( \xi \right) \circ (\mu +\rho
)-\rho },$ (resp. $\left( \co{\xi },k,n,\epsilon \left(
w_{a}\left( \xi \right) \right) \right) \mid _{\xi =w_{a}\left( \xi \right)
\circ (\nu +\rho _{a})-\rho _{a}}$ );

@@

$ch\left( L^{\mu }\right) =\frac{\sum_{w\in W}\epsilon (w)e^{w\circ (\mu
+\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{%
\mathrm{{mult}\left( \alpha \right) }}}=\frac{\Psi ^{\left( \mu \right) }}{%
\Psi ^{\left( 0\right) }}$ --- the Weyl-Kac formula;

$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
mult}\left( \alpha \right) }}=\Psi ^{\left( 0\right) }\quad $;

\noindent $\left( \mbox{resp. }R_{\af}:=\prod_{\alpha \in \Delta _{%
\af}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\af}\mathrm{%
\left( \alpha \right) }}=\Psi _{\af}^{\left( 0\right) }\right) $--- the
denominator;

$ L_{\frak{g}\downarrow \af}^{\mu }=\bigoplus
\limits_{\nu \in P_{\af}^{+}}b_{\nu }^{\left( \mu \right) }L_{\af}^{\nu }$
 --- the module decomposition with respect to $\af\longrightarrow \frak{g}$;

$b^{(\mu)}_{\nu}$ --- the branching coefficients,

\begin{equation}
  \label{eq:21}
  \sum_{\nu \in \bar{C_{\mathfrak{a}}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\af}}k_{\lambda
  }^{\left( \mu \right) }e^{\lambda };
\end{equation}

 $k_{\lambda}$ --- the anomalous branching coefficients, notice that
\begin{equation}
%  \label{eq:20}
  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in \bar{C}_{\mathfrak{a}};
\label{eq:21-1}
\end{equation}

$x_e=\frac{\left|\pi_{\mathfrak{a}} \Theta\right|^2}{\left|\Theta_{\mathfrak{a}}\right|^2}$ --- the embedding index.

\section{Recurrent relation for branching coefficients.}
\label{sec:recurr-form-branch}

Let $\af\subset \frak{g}$ be a regular subalgebra of $\frak{g.}$
Applying the Weyl-Kac character formula to the branching rule $\pi _{\af%
}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu
)}ch\left( L_{\af}^{\nu }\right) $ we get the relation connecting the
singular elements $\Psi ^{\left( \mu \right) }$ and $\Psi _{\left( \af%
\right) }^{\left( \nu \right) }$ :
\begin{eqnarray}
\pi _{\af}\left( \frac{\sum_{w \in W}\epsilon (w )e^{w
(\mu +\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}(1-e^{-\alpha })^{\mathrm{%
mult}(\alpha )}}\right) &=&\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu )}%
\frac{\sum_{w \in W_{\af}}\epsilon (w )e^{w (\nu +\rho _{%
\af})-\rho _{\af}}}{\prod_{\beta \in \Delta _{\af%
}^{+}}(1-e^{-\beta })^{\mathrm{mult}_{\af}(\beta )}},  \label{eq:4} \\
\pi _{\af}\left( \frac{\Psi ^{\left( \mu \right) }}{R}\right)
&=&\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\left( \frak{%
a}\right) }^{\left( \nu \right) }}{R_{\af}}.
\end{eqnarray}
where according to our notations $\Delta _{\af}^{+}$ is the set of
positive roots of the subalgebra $\af$ (it is convenient to choose them
from the positive root subspace of $\frak{g}$). Consider the root space $%
\frak{h}_{\perp \af}^{\ast }$ orthogonal to $\Delta _{\af}$,
\begin{equation*}
\frak{h}_{\perp \af}^{\ast }=:\left\{ \eta \in \frak{h}_{\frak{g}%
}^{\ast }|\forall \alpha \in \Delta _{\af};\alpha \bot \eta \right\} ,
\end{equation*}
and the roots (correspondingly -- positive roots) of $\frak{g}$ orthogonal
to $\Delta _{\af}$,
\begin{eqnarray*}
\Delta _{\af_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
\alpha \in \Delta _{\af};\alpha \bot \beta \right\} , \\
\Delta _{\af_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
}^{+}|\forall \alpha ^{+}\in \Delta _{\af}^{+};\alpha ^{+}\bot \beta
^{+}\right\} .
\end{eqnarray*}
Let $W_{\af_{\perp }}$ be the subgroup of $W$ generated by the
reflections $w _{\beta }$ for the roots $\beta \in \Delta _{\af%
_{\perp }}^{+}$ . The subsystem $\Delta _{\af_{\perp }}$ determines the
subalgebra $\af_{\perp }$ with the Cartan subalgebra $\frak{h}_{\af%
_{\perp }}$. Let
\begin{equation*}
\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \af}^{\ast
}|\forall \alpha \in \Delta _{\af}\cup \Delta _{\af_{\perp
}};\alpha \bot \eta \right\}
\end{equation*}
and consider the subalgebras
\begin{eqnarray*}
\widetilde{\af_{\perp }} &:&=\af_{\perp }\oplus \frak{h}_{\perp }
\\
\widetilde{\af} &:&=\af\oplus \frak{h}_{\perp }.
\end{eqnarray*}

The algebras $\af$ and $\af_{\perp }$ form an ''orthogonal pair''
of subalgebras in $\frak{g}$. For the Cartan subalgebras we have the
decomposition
\begin{equation}
\frak{h}=\frak{\frak{h}_{\af}}\oplus \frak{h}_{\af_{\perp }}\oplus
\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\af}}}\oplus \frak{h}_{%
\af_{\perp }}=\frak{\frak{h}_{\widetilde{\af_{\perp }}}}\oplus
\frak{h}_{\af}.
\end{equation}
For the subalgebras of the orthogonal pair $\left( \af,\af_{\perp
}\right) $ we consider the corresponding Weyl vectors, $\rho _{\af}$
and $\rho _{\af_{\perp }}$ , and\ form the so called ''defects'' $%
\mathcal{D}_{\af}$ and $\mathcal{D}_{\af_{\perp }}$ of the
injection:
\begin{equation}
\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho ,
\end{equation}
\begin{equation}
\mathcal{D}_{\af_{\perp }}:=\rho _{\af_{\perp }}-\pi _{\af%
_{\perp }}\rho .
\end{equation}
For the highest weight module $L_{\frak{g}}^{\mu }$ consider the singular
weights $\left( w(\mu +\rho )-\rho \right) \in \widehat{\Psi ^{\left( \mu
\right) }}$ and their projections to $h_{\widetilde{\af_{\perp }}%
}^{\ast }$ (additionally shifted by $-\mathcal{D}_{\af_{\perp }}$):
\begin{equation*}
\mu _{\widetilde{\af_{\perp }}}\left( w\right) :=\pi _{\widetilde{\frak{%
a}_{\perp }}}\left[ w(\mu +\rho )-\rho \right] -\mathcal{D}_{\af_{\perp
}},\quad w\in W.
\end{equation*}
Among the weights $\mu _{\widetilde{\af_{\perp }}}\left( w\right)
|_{w\in W}$ choose those located in the fundamental chamber $\overline{C_{%
\widetilde{\af_{\perp }}}}$ and let $U$ be the set of representatives $%
u $ for the classes $W/W_{\af_{\perp }}$ such that

\begin{equation}
U:=\left\{ u\in W|\quad \mu _{\widetilde{\af_{\perp }}}\left( u\right)
\in \overline{C_{\widetilde{\af_{\perp }}}}\right\} \quad .
\label{U-def}
\end{equation}
For the same set $U$ introduce the weights
\begin{equation*}
\mu _{\af}\left( u\right) :=\pi _{\af}\left[ u(\mu +\rho )-\rho %
\right] +\mathcal{D}_{\af_{\perp }}.
\end{equation*}

@@

\begin{definition}
\label{fan-definition} For the product
\begin{equation}
\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
_{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{\af%
}(\pi _{\af}\alpha )}=-\sum_{\gamma \in P_{\af}}s(\gamma
)e^{-\gamma }  \label{eq:6}
\end{equation}
consider the carrier $\Phi _{\af\subset \frak{g}}\subset P_{\af}$
of the function $s(\gamma )=\det \left( \gamma \right) $ :
\begin{equation}
\Phi _{\af\subset \frak{g}}=\left\{ \gamma \in P_{\af}|s(\gamma
)\neq 0\right\}   \label{eq:37}
\end{equation}
The ordering of roots in $\co{\Delta _{\af}}$ induce the
natural ordering of the weights in $P_{\af}$. Denote by $\gamma _{0}$
the lowest vector of $\Phi _{\af\subset \frak{g}}$ . The set
\begin{equation}
\Gamma _{\af\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
\af\subset \frak{g}}\right\} \setminus \left\{ 0\right\}
\label{fan-defined}
\end{equation}
is called the \textit{injection fan}.
\end{definition}

The main result is that the Weyl-Kac character formula (in terms of singular
elements) describes the particular case of a more general relation:

>>>>

\documentclass[12pt]{iopart}
%\usepackage{ucs}
%\usepackage{amsmath,amssymb,amsthm}
\usepackage{iopams,amssymb,amsthm}
%\usepackage{pb-diagram}
\usepackage{multicol}
%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
%\usepackage{cmap}
\usepackage{color}
\usepackage{graphicx}
%\usepackage{epstopdf}
%\usepackage{graphicx}
%\pagestyle{plain}
%\usepackage[unicode,verbose,plainpages=false]{hyperref}
\usepackage{hyperref}

@@

\newtheorem{statement}{Statement}
\newtheorem{theorem}{Theorem}
%\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}{Lemma}
\newtheorem{mynote}{Note}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}

@@

\title{Recursive algorithms and branching for nonmaximal embeddings}
\author{V D Lyakhovsky$^1$ and A A Nazarov$^2$}
\address{$^{1,2}$ Theoretical Department, SPb State University,
198904, Sankt-Petersburg, Russia }
\eads{$^1$ \mailto{lyakh1507@nm.ru}, $^2$ \mailto{antonnaz@gmail.com}}

\begin{abstract}
  Recurrent relations for branching coefficients in affine Lie algebras
  integrable highest weight modules are studied. The decomposition algorithm
  based on the injection fan technique is developed for the case of reductive
  subalgebra. In particular we consider the situations where
  the Weyl denominator becomes singular with respect to the subalgebra.
  We study the modifications of the injection fan technique and demonstrate
  that for any reductive subalgebra it is possible to define the
  "subtracted fan" -- the tool that describes
  explicitly the recurrent properties of branching coefficients.
  Possible applications of subtracted fans in CFT models are considered.
\end{abstract}
\ams{17B67, 17B10}
\submitto{\JPA}
%\maketitle

@@

There exist different approaches to deal with the branching coefficients. Some of them use the BGG
resolution \cite{bernstein1975differential} (for Kac-Moody algebras the algorithm is described in
\cite{kac1990idl},\cite{wakimoto2001idl}), the Schur function series \cite{fauser2006new}, the BRST
cohomology \cite{Hwang:1994yr}, Kac-Peterson formulas \cite{kac1990idl,quella2002branching} or the
combinatorial methods applied in \cite{feigin707principal}.

Usually only the maximal reductive subalgebras $\frak{a} \subset \frak{g} $ are considered since the case of non-maximal subalgebra
can be obtained using the chain of maximal injections. In this paper we find out that the recurrent properties
for branching coefficients can be explicitly formulated for an arbitrary reductive subalgebra.
The principal point is to consider the subalgebra $\af$ together with its
counterpart $\afb$ "orthogonal" to $\af$ with respect to the Killing form.
For any reductive $\af$ the subalgebra $\afb \subset \frak{g} $ is a regular and reductive.
For a highest weight module $L^{\left( \mu \right)}$ and orthogonal pair of subalgebras
$\left(  \af, \afb \right)$ we consider
%In the the group algebra $\mathcal{E}\left( \frak{g} \right)$ we consider
the so called singular element $\Psi^{\left( \mu \right)}$ (the numerator
in the Weyl character formula
$ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left( 0\right) }}$, see for example \cite{humphreys1978rth})
the Weyl denominator $\Psi ^{\left( 0\right) }_{\afb}$ and the projection
$\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}=\pi_{\af}\frac{\Psi ^{\left( \mu \right) }_{\frak{g}}}{\Psi ^{\left( 0\right) }_{\afb}}$.
We prove that for any highest weight module $L^{\left( \mu \right)}$ and orthogonal pair of subalgebras
$\left(  \af, \afb \right)$ the element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$ has a decomposition with respect to
the set of Weyl numerators of $\afb$.
This decomposition provides the possibility to construct the recurrent property for the branching coefficients corresponding
to the injection $\frak{a} \longrightarrow \frak{g} $.
This property is formulated in
terms of a specific element of the group algebra $\mathcal{E}\left( \frak{g} \right)$ called "the subtracted injection fan".
Using this tool we formulate a simple and
explicit algorithm for branching coefficients computations applicable for an arbitrary (maximal or non-maximal)
subalgebras of finite-dimensional and affine Lie algebras.
In the case of maximal embedding the corresponding fan becomes unsubtracted and the recurrent relations described
earlier (see the paper \cite{ilyin812pbc}
and the references therein) are reobtained.

@@

The paper is organised as follows. In the subsection \ref{sec:notation}  we fix the general notations.
In the Section \ref{sec:recurr-form-branch} we derive the decomposition formula for
the subtracted recurrent formula for anomalous
branching coefficients and describe the decomposition algorithm for integrable highest weight modules
$L_{\mathfrak{g}}$ with respect to a reductive subalgebra $\mathfrak{a}\subset \mathfrak{g}$
(subsection \ref{sec:algorithm}). In the Section \ref{sec:finite-dimens-lie} we present several
simple examples for finite-dimensional Lie algebras. The affine Lie algebras and their applications in
CFT models are considered in Section \ref{sec:phys-appl}.
Possible further developments are discussed (Section \ref{sec:conclusion}).

@@

$\co{\Delta}$ , $\left( \co{\Delta _{\af}}%
\right)$ --- the finite root system of the subalgebra $\co{%
\frak{g}}$ (resp. $\co{\af}$);

@@

%$M \left( \mbox{resp. }M_{\af}\right) :=$

%\noindent $=\left\{
%\begin{array}{c}
%\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}^{\vee }\mbox{ }\left( \mbox{resp. }%
%\sum_{i=1}^{r}\mathbf{Z}\alpha _{\left( \af\right) i}^{\vee }\right)
%\mbox{for untwisted algebras or }A_{2r}^{\left( 2\right) }, \\
%\sum_{i=1}^{r}\mathbf{Z}\alpha _{i}\mbox{ }\left( \mbox{resp. }\sum_{i=1}^{r}%
%\mathbf{Z}\alpha _{\left( \af\right) i}\right) \mbox{for }A_{r}^{\left(
%u\geq 2\right) }\mbox{ and }A\neq A_{2r}^{\left( 2\right) },
%\end{array}
%\right\} ;$\\

%$\widehat{\Psi ^{\left( \mu \right) }}$ $\left( \widehat{\Psi _{\left( \frak{%
%a}\right) }^{\left( \nu \right) }}\right) $ --- the set of singular weights $%
%\xi \in P$ $\left( \mbox{resp. }\in P_{\af}\right) $ for the module $%
%L^{\mu }$ $\left( \mbox{resp. }L_{\af}^{\nu }\right) $ with the
%coordinates $\left( \co{\xi },k,n,\epsilon \left( w\left( \xi
%\right) \right) \right) \mid _{\xi =w\left( \xi \right) \circ (\mu +\rho
%)-\rho },$ (resp. $\left( \co{\xi },k,n,\epsilon \left(
%w_{a}\left( \xi \right) \right) \right) \mid _{\xi =w_{a}\left( \xi \right)
%\circ (\nu +\rho _{a})-\rho _{a}}$ );

@@

$ch\left( L^{\mu }\right) =\frac{\sum_{w\in W}\epsilon (w)e^{w\circ (\mu
+\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{%
\mathrm{{mult}\left( \alpha \right) }}}$ --- the Weyl-Kac formula;

$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
mult}\left( \alpha \right) }}\quad $
$\left( \mbox{resp. }R_{\af}:=\prod_{\alpha \in \Delta _{%
\af}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\af}\mathrm{%
\left( \alpha \right) }}\right) $--- the
denominator.

\section{Recurrent relations for branching coefficients.}
\label{sec:recurr-form-branch}

Consider the integrable module $L^{\mu }$
of $\frak{g}$ with the highest weight $\mu $ and
let $\af\subset \frak{g}$ be a reductive subalgebra of $\frak{g}$.
With respect to $\af$ the module $L^{\mu }$ is completely reducible,
\begin{equation*}
 L_{\frak{g}\downarrow \af}^{\mu }=\bigoplus
\limits_{\nu \in P_{\af}^{+}}b_{\nu }^{\left( \mu \right) }L_{\af}^{\nu }.
\end{equation*}
Using the projection operator $\pi_{\af}$ (to the weight space $\frak{h_a}^*$)
one can  rewrite this decomposition in terms of formal characters:
\begin{equation}
\label{branching1}
 \pi _{\af}\circ ch\left( L^{\mu }\right)
 =\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu)}ch\left( L_{\af}^{\nu }\right) .
\end{equation}
We are interested in branching coefficients $b^{(\mu)}_{\nu}$.

\subsection{Orthogonal subalgebra and injection fan.}
\label{subsec:branching-orthog-pair}

In this subsection we shall introduce some simple constructions that will be used
in our studies of branching and in particular the "orthogonal partner" $\afb$ for a
reductive subalgebra $\af$  in  $\gf$.

In the Weyl-Kac formula both numerator and denominator  can be considered
as formal elements containing the singular weights of the Verma modules $V^{\xi}$
with the highest weights $\xi=\mu$ and $\xi=0$ \cite{humphreys1978rth}.
We attribute singular numerators to the corresponding integrable modules $L^{\mu }$
and $L_{\af}^{\nu }$:
\begin{equation*}
\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu +\rho )-\rho },
\end{equation*}
\begin{equation*}
\Psi _{ \af}^{\left( \nu \right) }:=
\sum\limits_{w\in W_{\af}}\epsilon (w)e^{w\circ (\nu +\rho
_{_{\af}})-\rho _{_{\af}}}.
\end{equation*}
and use the Weyl-Kac formula in the form
\begin{equation}
\label{Weyl-Kac2}
ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}
{\Psi ^{\left( 0 \right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.
\end{equation}

Applying formula (\ref{Weyl-Kac2}) to the branching rule (\ref{branching1})
we get the relation connecting the
singular elements $\Psi ^{\left( \mu \right) }$ and $\Psi _{ \af}^{\left( \nu \right) }$ :
\begin{eqnarray}
\nonumber
\pi _{\af}\left( \frac{\sum_{w \in W}\epsilon (w )e^{w
(\mu +\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}(1-e^{-\alpha })^{\mathrm{%
mult}(\alpha )}}\right) &=&\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu )}%
\frac{\sum_{w \in W_{\af}}\epsilon (w )e^{w (\nu +\rho _{%
\af})-\rho _{\af}}}{\prod_{\beta \in \Delta _{\af%
}^{+}}(1-e^{-\beta })^{\mathrm{mult}_{\af}(\beta )}},  \label{eq:4} \\
\pi _{\af}\left( \frac{\Psi ^{\left( \mu \right) }}{R}\right)
&=&\sum_{\nu \in P_{\af}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{ \frak{%
a}}^{\left( \nu \right) }}{R_{\af}}.
\end{eqnarray}
Here $\Delta _{\af}^{+}$ is the set of
positive roots of the subalgebra $\af$ (without loss of generality we consider
them as vectors from the positive root space $\frak{h}^{\ast  +}$ of $\frak{g}$).

Consider the root subspace
$\frak{h}_{\perp \af}^{\ast }$ orthogonal to the roots in $\Delta _{\af}$,
\begin{equation*}
\frak{h}_{\perp \af}^{\ast }=:\left\{ \eta \in \frak{h}^{\ast }
|\forall \alpha \in \Delta _{\af};\alpha \bot \eta \right\} ,
\end{equation*}
and the roots (correspondingly -- positive roots) of $\frak{g}$ orthogonal
to $\Delta _{\af}$,
\begin{eqnarray*}
\Delta _{\af_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
\alpha \in \Delta _{\af};\alpha \bot \beta \right\} , \\
\Delta _{\af_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
}^{+}|\forall \alpha ^{+}\in \Delta _{\af}^{+};\alpha ^{+}\bot \beta
^{+}\right\} .
\end{eqnarray*}
Let $W_{\af_{\perp }}$ be the subgroup of $W$ generated by the
reflections $w _{\beta }$ for the roots $\beta \in \Delta _{\af%
_{\perp }}^{+}$ . The subsystem $\Delta _{\af_{\perp }}$ determines the
subalgebra $\af_{\perp }$ with the Cartan subalgebra $\frak{h}_{\af%
_{\perp }}$. Let
\begin{equation*}
\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \af}^{\ast
}|\forall \alpha \in \Delta _{\af}\cup \Delta _{\af_{\perp
}};\alpha \bot \eta \right\}
\end{equation*}
and consider the subalgebras
\begin{eqnarray*}
\widetilde{\af_{\perp }} &:&=\af_{\perp }\oplus \frak{h}_{\perp }
\\
\widetilde{\af} &:&=\af\oplus \frak{h}_{\perp }.
\end{eqnarray*}
Algebras $\af$ and $\af_{\perp }$ form the ''orthogonal pair''
$\left( \af,\af_{\perp}\right) $
of subalgebras in $\frak{g}$.

For the Cartan subalgebras we have the decomposition
\begin{equation}
\frak{h}=\frak{\frak{h}_{\af}}\oplus \frak{h}_{\af_{\perp }}\oplus
\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\af}}}\oplus \frak{h}_{%
\af_{\perp }}=\frak{\frak{h}_{\widetilde{\af_{\perp }}}}\oplus
\frak{h}_{\af}.
\end{equation}
For the subalgebras of an orthogonal pair $\left( \af,\af_{\perp
}\right) $ we consider the corresponding Weyl vectors, $\rho _{\af}$
and $\rho _{\af_{\perp }}$ , and\ form the so called ''defects'' $%
\mathcal{D}_{\af}$ and $\mathcal{D}_{\af_{\perp }}$ of the
injection:
\begin{equation}
\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho ,
\end{equation}
\begin{equation}
\label{defect-perp}
\mathcal{D}_{\af_{\perp }}:=\rho _{\af_{\perp }}-\pi _{\af%
_{\perp }}\circ\rho .
\end{equation}
For the highest weight module $L_{\frak{g}}^{\mu }$ consider the singular
weights $\left\{\left( w(\mu +\rho )-\rho \right)|w  \in W \right\}$ and
their projections to $h_{\widetilde{\af_{\perp }}}^{\ast }$ (additionally
shifted by the defect $-\mathcal{D}_{\af_{\perp }}$):
\begin{equation*}
\mu _{\widetilde{\af_{\perp }}}\left( w\right) :=\pi _{\widetilde{\frak{%
a}_{\perp }}}\circ\left[ w(\mu +\rho )-\rho \right] -\mathcal{D}_{\af_{\perp
}},\quad w\in W.
\end{equation*}
Among the weights $\left\{\mu _{\widetilde{\af_{\perp }}}\left( w\right)
|w\in W\right\}$ choose those located in the fundamental chamber $\overline{C_{%
\widetilde{\af_{\perp }}}}$ and let $U$ be the set of representatives $%
u $ for the classes $W/W_{\af_{\perp }}$ such that

\begin{equation}
U:=\left\{ u\in W|\quad \mu _{\widetilde{\af_{\perp }}}\left( u\right)
\in \overline{C_{\widetilde{\af_{\perp }}}}\right\} \quad .
\label{U-def}
\end{equation}
For the same set $U$ introduce the weights
\begin{equation*}
\mu _{\af}\left( u\right) :=\pi _{\af}\circ\left[ u(\mu +\rho )-\rho %
\right] +\mathcal{D}_{\af_{\perp }}.
\end{equation*}
To simplify the form of relations we shall now on omit the sign "$\circ$" in projected
weights.

@@

\begin{definition}
\label{fan-definition} For the product
\begin{equation}
\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
_{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{\af%
}(\pi _{\af}\alpha )}=-\sum_{\gamma \in P_{\af}}s(\gamma
)e^{-\gamma }  \label{eq:6}
\end{equation}
consider the carrier $\Phi _{\af\subset \frak{g}}\subset P_{\af}$
of the function $s(\gamma )=\det \left( \gamma \right) $ :
\begin{equation}
\Phi _{\af\subset \frak{g}}=\left\{ \gamma \in P_{\af}|s(\gamma
)\neq 0\right\}   \label{eq:37}
\end{equation}
The ordering of roots in $\co{\Delta _{\af}}$ induce the
natural ordering of the weights in $P_{\af}$. Denote by $\gamma _{0}$
the lowest vector of $\Phi _{\af\subset \frak{g}}$ . The set
\begin{equation}
\Gamma _{\af\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
\af\subset \frak{g}}\right\} \setminus \left\{ 0\right\}
\label{fan-defined}
\end{equation}
is called the \textit{injection fan}.
\end{definition}
In the next subsection we shall see how the injection fan defines the recurrent
properties of branching coefficients. It must be noticed that the injection fan is
the universal instrument that depend only on the injection.

\subsection{Decomposing the singular element.}
\label{subsec:decomp-sing-element}

Now we shall prove that the Weyl-Kac character formula (in terms of singular
elements) describes the particular case of a more general relation:
